Untargeted control doc

### 2023-09-27 untargeted/paruntargeted_control.Rmd
Annotated Nit pos, needs rescuing still

polarity <- "pos"
# polarity <- "neg"
amendment <- "Amm"
# amendment <- "Nit"
# amendment <- "GMP"
# amendment <- "Arg"
IS_type <- "noIS"
# IS_type <- "wIS"

>>>>

polarity <- "pos"
# polarity <- "neg"
# amendment <- "Amm"
amendment <- "Nit"
# amendment <- "GMP"
# amendment <- "Arg"
IS_type <- "noIS"
# IS_type <- "wIS"
